### 2022-04-13 greta/mcmc.Rmd
1-rep, with transistion
100 reps (again)
different test/train sets!

```{r}
library(tidyverse)
set.seed(1234567)

np.clip <- function(x, a, b) {
  if(x < a) return(a)
  if(x > b) return(b)
  x
}

# View the bistable curve: 
# curve( (0.75 - x)**2 * (0.25 - x), 0, 1)

@@

sims <- purrr::map_dfr(1:10, \(i) simulate(), .id = "i")
sims |> ggplot(aes(t, N, group=i)) + geom_line(alpha=0.06)
```

```{r}
gsims <- sims |> group_by(i) |> mutate(xt1 = lead(N)) |> filter(t<max(t))

@@

```{r}
posterior_samples <- 
  bind_rows(map(draws, as_tibble)) %>% 
  sample_n(100)
posterior_sims <- posterior_samples %>%
  purrr::transpose() %>%
  map_dfr(function(q) simulate() ,.id = "i")

bind_rows(sims, posterior_sims, .id = "model")|> 
  ggplot(aes(t, N, col=model, group=interaction(model,i))) +
           geom_line(alpha=0.3)

@@

@@

# Score just the 1st replicate "true" observations
observed <- sims |> filter(i == 1) |> pull(N)
scores(observed, dat)

@@

rep_scores <- sims |> group_by(i) |> group_map(~ scores(.x$N, dat)) |> bind_rows()
```

>>>>

```{r}
library(tidyverse)
library(greta)
library(bayesplot)

set.seed(4242)
train_reps <- 10
train_t_max <- 250
test_t_max <- 250
test_reps <- 100

np.clip <- function(x, a, b) {
  if(x < a) return(a)
  if(x > b) return(b)
  x
}
```

```{r}
# View the bistable curve: 
# curve( (0.75 - x)**2 * (0.25 - x), 0, 1)

@@

train <- purrr::map_dfr(1:train_reps, \(i) simulate(t_max=train_t_max), .id = "i")
test <- purrr::map_dfr(1:test_reps, \(i) simulate(t_max=test_t_max), .id = "i")

## show training data
train |> ggplot(aes(t, N, group=i)) + geom_line(alpha=0.2)
```

```{r}
gsims <- train |> group_by(i) |> mutate(xt1 = lead(N)) |> filter(t<max(t))

@@

```{r}
posterior_samples <- 
  bind_rows(map(draws, as_tibble)) %>% 
  sample_n(100)
posterior_sims <- posterior_samples %>%
  purrr::transpose() %>%
  map_dfr(function(q) simulate(t_max = test_t_max) ,.id = "i")

bind_rows(test, posterior_sims, .id = "model")|> 
  ggplot(aes(t, N, col=model, group=interaction(model,i))) +
           geom_line(alpha=0.3)

@@

```{r}
true <- tibble(a = 0.75, b = 0.25, sigma = 1e-2) |> gather(variable, value)

posterior_samples  |> gather(variable, value) |> ggplot() + 
  geom_histogram(aes(value), bins = 30)  +
  geom_vline(data = true, aes(xintercept = value), col = "red", lwd = 1) + 
  facet_wrap(~variable, scales = "free")
```

@@

# Score just the 1st replicate "true" observations
observed <- test |> filter(i == 1) |> pull(N)
scores(observed, dat)

@@

rep_scores <- test |> group_by(i) |> group_map(~ scores(.x$N, dat)) |> bind_rows()
```
